Stringy canonical forms and binary geometries from associahedra, cyclohedra and generalized permutohedra

### 2020-06-27 draft_ABP.tex
Updates from Overleaf

\documentclass[hidelinks,12pt]{article}
\pdfoutput=1
\usepackage{jheppub}

%\input epsf.sty
%\topmargin -.1cm
%\textheight 21cm
%\oddsidemargin 0.15cm 
%\textwidth 14cm
\usepackage{cite,comment}
\usepackage{epsfig,amssymb,euscript,xspace,xcolor}
\usepackage{amsfonts,amssymb,amsmath,mathtools,empheq,amsthm,hyperref,graphicx,paralist}
\usepackage{mathrsfs,float}  
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{arrows}
%\usepackage[T1]{fontenc} 
\usepackage{tikz,caption,subcaption,marvosym} 
\usetikzlibrary{decorations.markings,arrows,snakes}
\usepackage[belowskip=-15pt,aboveskip=0pt]{caption}
%\usepackage[skip=10pt]{caption} % example skip set to 2pt

@@

\usepackage[titles]{tocloft}
\renewcommand{\cftdot}{} %Don't want dots in TOC

@@

\usepackage{hyperref,cite}
\hypersetup{linktocpage, colorlinks=true,linkcolor= blue,citecolor=blue,urlcolor=lightblue}

@@

\textwidth 16.9cm
\oddsidemargin -.25cm

@@

\renewcommand{\theequation}{\thesection.\arabic{equation}}
\renewcommand{\theequation}{\arabic{equation}}

@@

\definecolor{wvvxds}{rgb}{0.396078431372549,0.3411764705882353,0.8235294117647058}
\definecolor{dbwrru}{rgb}{0.8588235294117647,0.3803921568627451,0.0784313725490196}
\definecolor{dtsfsf}{rgb}{0.8274509803921568,0.1843137254901961,0.1843137254901961}
\definecolor{wrwrwr}{rgb}{0.3803921568627451,0.3803921568627451,0.3803921568627451}
\definecolor{cqcqcq}{rgb}{0.7529411764705882,0.7529411764705882,0.7529411764705882}
\definecolor{rvwvcq}{rgb}{0.08235294117647059,0.396078431372549,0.7529411764705882}
\makeatletter
\newenvironment{calc}{\allowdisplaybreaks\start@align\@ne\st@rredtrue\m@ne}
{\addtocounter{equation}{1}\tag{\theequation}\endalign}
% for calculations/derivations---only last line gets an equation number, 
%	and allows page breaks for long calculations

@@

@@

\baselineskip 24pt

\begin{center}

{\Large \bf Stringy canonical forms and binary geometries from associahedra, cyclohedra and generalized permutohedra}

\end{center}

\vskip .5cm
\medskip

\vspace*{4.0ex}

\baselineskip=15 pt

\centerline{\large \rm  {\bf Song He$^{a, b}$, Zhenjie Li$^{a, b}$, Prashanth Raman$^{a, c,d}$, Chi Zhang$^{a, b}$ } }

\vspace*{4.0ex}
{\it ~ $^a$ CAS Key Laboratory of Theoretical Physics, Institute of Theoretical Physics, Chinese Academy}

{\it of Sciences, Beijing 100190, China}

{\it ~$^b$ School of Physical Sciences, University of Chinese Academy of Sciences, No.19A Yuquan Road,}

{\it Beijing 100049, China}

{\it ~$^c$ Institute of Mathematical Sciences, Taramani, Chennai 600 113, India}

{\it ~$^d$ Homi Bhabha National Institute, Anushakti Nagar, Mumbai 400085, India}

\vspace*{1.0ex}
\centerline{\it ~E-mail : songhe@itp.ac.cn, lizhenjie@itp.ac.cn, prashanthr@imsc.res.in, zhangchi@itp.ac.cn} 
\vspace*{5.0ex}
\centerline{\bf Abstract} \bigskip

Stringy canonical forms are a class of integrals that provide $\alpha'$-deformations of the canonical form of any polytopes. For generalized associahedra of finite-type cluster algebras, there exist completely rigid stringy integrals, whose configuration spaces are the so-called binary geometries, and for classical types are associated with (generalized) scattering of particles and strings. In this paper we propose a large class of rigid stringy canonical forms for another class of polytopes, generalized permutohedra, which also include associahedra and cyclohedra as special cases (type $A_n$ and $B_n$ generalized associahedra). Remarkably, we find that the configuration spaces of such integrals are also binary geometries, which were suspected to exist for generalized associahedra only. For any generalized permutohedron that can be written as Minkowski sum of coordinate simplices, we show that its rigid stringy integral factorizes into products of lower integrals for massless poles at finite $\alpha'$, and the configuration space is binary although the $u$ equations take a more general form than those ``perfect'' ones for cluster cases. Moreover, we provide an infinite class of examples obtained by degenerations of type $A_n$ and $B_n$ integrals, which have perfect $u$ equations as well. Our results provide yet another family of generalizations of the usual string integral and moduli space, whose physical interpretations remain to be explored.

\vfill \eject

\baselineskip=18pt

\tableofcontents

\newpage

@@

The $u$ equations are:
\begin{align*}
1-\tilde u_{[0,l]}&=\left(\prod_{i=0}^{l-1} \prod_{j=i+1}^{k+1}  \tilde u_{[0,i]\cup [j,n]} \prod_{j=i+1}^{l+1} \tilde u_{[0,i]\cup [j,n]}\right) \left(\prod_{i=1}^{l+1} \prod_{j=l+1}^{n}\tilde u_{[i,j]} \right) \left(\prod_{i=1}^{k+1} \tilde u_{[i,n]} \right),\\\\
1-\tilde u_{[m+2,n]}&=\left( \prod_{j=0}^{m}\tilde u_{[0,j]} \prod_{i=1}^{n-m-1}\tilde u_{[0,m+i]}^2 \right) \left( \prod_{i=m+1}^{n-1}\prod_{j=1}^{m+1}\tilde u_{[j,i]} \right) \left(\prod_{j=0}^{k-m-2} \prod_{i=1}^{m} \tilde u_{[0,i]\cup [3+j+m, n]} \prod_{i= m+1}^{j+m+1} \tilde u_{[0,i]\cup [3+j+m,n]}^2 \right) \\\\
1-\tilde u_{K_{l,m}}&=\left(\prod_{a=0}^1\prod_{i=l+1}^{n}\tilde u_{[a,i]}\right) \left(\prod_{{\tiny {K_{l',m'} \not\subset K_{l,m}}\atop{K_{l,m} \not\subset K_{l',m'}} }} \tilde u_{K_{l',m'}}^{(l',m')||(l,m)}\right)\left(\prod_{j=2}^{m+1} \prod_{i=l+1}^{n} \tilde u_{[j,i]} \right)\times 
\begin{cases}
 1, ~{\rm if} ~ l=m  \\
 \prod_{i=0}^{l+1} \prod_{j=m+1}^n \tilde u_{[i,j]},~ {\rm if}~l \neq m
\end{cases}
\end{align*}
where $(l',m')||(l,m)$ is the compatability degree of $K_{l,m}$ with respect to $K_{l',m'}$ in $\mathscr B_n$ with the understanding that $\tilde u_{[0,n]}=1$ and the other $u$ equations are corresponding $u$ equations for $\mathscr A_n$ in new variables.

@@

\section{Stringy canonical forms and binary geometries for generalized permutohedra}
In this section we shall argue that a large class of generalized permutohedra which are realised as degenerations of permutohedron ${\mathscr P_n}$ are binary geometries. Before we proceed we shall review some details about the generalized permutohedra \cite{Postnikov:2005,Postnikov:2006} which we shall use throughout the paper.
\subsection{Generalized permutohedra}\label{GP}
A generalized permutohedron is a polytope that can obtained be as Minkowski sums and differences of co-ordinate simplices.

Let $\Delta_{[0,n]} = \operatorname{ConvexHull}(e_1,\dots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
\bea
{\mathscr P_n}(\{y_I \})= \sum y_I . \Delta_I  
\eea
for some collection of subsets $I \in [0,n]$.
We shall restrict ourselves to the large class of generalized permutohedra which admit such a realisation only as Minkowski sums except translations i.e, $y_I \ge 0$ for all non-singlets $I$\footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s. We allow $y_I$ for singlets to be  negative as it is only a translation and to connect with \eqref{intgenperm}.} which are called Nestohedra. Throughout the paper we shall mean Nestohedra or products of Nestohedra whenever we refer to generalized permutohedra.

The combinatorial structure of the generalized permutohedron ${\mathscr P_n(\{y_I\})}$ (Nestohedra) is independent of $y_I$ and depends only on the collection of subsets $I \in [0,n]$ of the  building set ${\mathbf B}$, which is 
a collection of non-empty subsets of $[0,n]$ satisfying the following: %is called a building set ${\mathbf B} if it satisfies the following:
\begin{compactenum}[\quad (1)]
    \item If $I,J \in {\mathbf B}$ and $I \cap J \neq \varnothing $, then $I \cup J \in {\mathbf B}$.
    \item ${\mathbf B}$ contains all singletons $\{ i\}$ for $i \in S$.
\end{compactenum}
Here are some interesting examples of generalized permutohedra:
\begin{itemize}
    \item  If ${\mathbf B}= \{[i] | i=0,\dots,n \}$ is the complete flag of intervals, then ${\mathscr P_n(\{y_I\})}$ is the Stanley-Pitman polytope or Hypercube.
    \item If ${\mathbf B}$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr P_n(\{y_I\})}$ is the usual permutohedron ${\mathscr P_n}$. 
    \item If ${\mathbf B}=\{ [i,j] | 0\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n(\{y_I\})}$ is the associahedron ${\mathscr A_n}$. 
    \item If  $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$ is the set of cyclic intervals, then ${\mathscr P_n(\{y_I\})}$ is the cyclohedron ${\mathscr B_n}$.
    \item Let $\Gamma$ be a graph on the vertex set $[0,n]$. Let us assume that ${\mathbf B} = {\mathbf B}(\Gamma)$ is the set of subsets $I \in [0,n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr P_n(\{y_I\})}$ is a graph associahedron.
\end{itemize}

\paragraph{Nested complex} To describe the combinatorial structure we need the notion of {\it Nested complex}. We shall only summarize the necessary results here and let the reader interested in the details to refer \cite{Postnikov:2005,Postnikov:2006}.
A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\dots, J_k \in \mathbf N$ their union $J_1 \cup \cdots \cup J_k$ is not in $\mathbf B$.
    \item ${\mathbf N}$ contains all maximal elements of $\mathbf B$.
\end{compactenum}
The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.
\paragraph*{Facial structure} 
Let us assume that the set ${\mathbf B}$ associated with a generalized permutohedron ${\mathscr P_n(\{y_I\})}$ is a building set on $[0,n]$. \emph{Then the poset of faces ${\mathscr P_n(\{y_I\})}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$}.

In particular, it means that (1) the number of facets $N$ of the generalized permutohedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal element, and (2) two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect i.e., are {\it compatible} with each other if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \varnothing ~{\text and} ~ I \cup J \notin {\mathbf B}$.

@@

% Text Node
\draw (401.67,176.33) node [anchor=north west][inner sep=0.75pt]   [align=left] {01};
% Text Node
\draw (461,212) node [anchor=north west][inner sep=0.75pt]   [align=left] {0};
% Text Node
\draw (412,109) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
% Text Node
\draw (463,78) node [anchor=north west][inner sep=0.75pt]   [align=left] {12};
% Text Node
\draw (527,101) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
% Text Node
\draw (523,179) node [anchor=north west][inner sep=0.75pt]   [align=left] {02};
% Text Node
\draw (268,204) node [anchor=north west][inner sep=0.75pt]   [align=left] {0};
% Text Node
\draw (226,96) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
% Text Node
\draw (310,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {12};
% Text Node
\draw (336,163) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
% Text Node
\draw (203,160) node [anchor=north west][inner sep=0.75pt]   [align=left] {01};
% Text Node
\draw (262,235) node [anchor=north west][inner sep=0.75pt]   [align=left] {(a)};
% Text Node
\draw (454,235) node [anchor=north west][inner sep=0.75pt]   [align=left] {(b)};
% Text Node
% \draw (155,263) node [anchor=north west][inner sep=0.75pt]   [align=left] {Figure showing the compatible\textbackslash incompatible facets of the 2d associahedron  \\ and permutohedron as generalized permutohedra};
\end{tikzpicture}
\end{center}
\caption{Compatible\textbackslash incompatible facets of the 2d associahedron (a) and permutohedron (b) as generalized permutohedra}
\end{figure}

@@

Generalized permutohedra have big polyhedra which are simplices. Thus its quite natural to wonder if the associated $u$ variables satisfy some kind of $u$ equations. We claim and we shall show in the next section that this indeed the case. Further we show that all these polytopes are binary geometries even though some of them do not admit perfect $u$ equations.

@@

%We have seen that any $n$-dimensional generalized permutohedron can be constructed by a Minkowski sum of simplices labeled by subsets in the building set $\mathbf{B}$, which satisfy the conditions given above. 
As we mentioned earlier, one can write down a natural stringy integral \eqref{intgenperm} for generalized permutahedron $\mathscr{P}(\bf B)$,
%it is a highly non-trivial fact about generalized permutohedra that the number of facets is given by $N=n+m$, where $m$ is the number of non-singletons in $\bf B$. 
%because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
and its polytope is given by the Minkowski sum
\[
	\mathscr P_n(\{-S_I\,|\,I\in \mathbf B,\,|I|>1\}) =- \sum_{I\in\mathbf{B},|I|>1}S_I.\Delta_I,
\]
where $\Delta_I=\operatorname{ConvexHull}
(\{e_i\}_{i\in I})$ is the coordinate simplex in $(S_0,\dots,S_n)$-space, so the equation of the facet labeled by $I$ is given by eq.\eqref{eqoffacet}:
\begin{equation}\label{GPfacet}
	F_I:=\sum_{J\subset I,J\in\mathbf{B}}S_J=0.
\end{equation}
From the previous subsection we know that the big polyhedron of a generalized permutohedron is a simplex.
Therefore, we can write down the matrix $W^J_A$ of the facets and obtain  
\[
S_J=F_A(W^{-1})^A_J
\]
and 
its $u$ variables 
\[ u_A=\prod_J x_J^{(W^{-1})^A_J}. \]

Within generalized permutohedra, the original permutohedron is quite simple and important because any other generalized permutohedron can be obtained as a degenerated of the permutohedron.
The building set of the $n$-dimensional permutohedron $\mathscr P_n$ is 
the set of all non-empty subsets of $[0,n]$. 
To get $u$ equations, we should solve for $S_J$ from $F_J$ in eq.\eqref{GPfacet}, the 
solution for the permutohedron $\mathscr P_n$ is 
\begin{equation}\label{SinF}
	S_I=\sum_{J\subset I} (-1)^{|J|-|I|}F_J,
\end{equation}
This gives us the following ABHY polytope:
setting 
$S_I=-C_I$ for any non-singleton $I\in \mathscr P_n$, where $C_I$ are positive 
constants, and the polytope is given by the alternating sum
\begin{equation}\label{ABHY}
	F_I\geq 0,\quad -C_I=\sum_{J\neq \varnothing,J\subset I}(-1)^{|J|-|I|}F_J
\end{equation}
in the $\{F_I\}$-space.
By eq.\eqref{deffacet}, this polytope is the $n$-dimensional 
permutohedron $\mathscr P_n(\{C_I\})$, and it is nice that it admits a simple ABHY-like realization.
The ABHY construction of any generalized permutohedron can be obtained by 
setting $C_I=0$ in $\mathscr P_n(\{C_I\})$ for all $I$ not in its building set.

@@

Moreover, since we have found a variety of such geometries with perfect $u$ equations from degenerating ${\mathscr A}_n$ and ${\mathscr B}_n$, it'd be very interesting to explore more cases with perfect $u$ equations from degenerations of other types, {\it e.g.} ${\mathscr C_n}$ and ${\mathscr D_n}$. Along this direction, an intriguing possibility is to classify binary geometries with perfect $u$ equations from degenerating cluster cases; since any product of such geometries still has perfect $u$ equations, this amounts to find all elementary, non-factorizing geometries with perfect $u$ equations. More importantly,  what are the possible interpretations of these degenerations from cluster algebra; even for ${\mathscr A}_{n-3}$, what are the meaning of these degenerations of ${\cal M}_{0,n}$ and the string integrals?

>>>>

\documentclass[hidelinks,12pt]{article}
\pdfoutput=1

%\input epsf.sty
%\topmargin -.1cm
%\textheight 21cm
%\oddsidemargin 0.15cm 
%\textwidth 14cm
\usepackage{comment}
\usepackage{epsfig,amssymb,euscript,xspace,xcolor}
\usepackage{amsfonts,amssymb,amsmath,mathtools,empheq,amsthm,graphicx,paralist}
\usepackage{mathrsfs,float}  
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{arrows}
%\usepackage[T1]{fontenc} 
\usepackage{tikz,caption,subcaption,marvosym} 
\usetikzlibrary{decorations.markings,arrows,snakes}
\usepackage[belowskip=-15pt,aboveskip=0pt]{caption}
%\usepackage[skip=10pt]{caption} % example skip set to 2pt

@@

% \usepackage[titles]{tocloft}
% \renewcommand{\cftdot}{} %Don't want dots in TOC

@@

% \usepackage{hyperref}
% \hypersetup{linktocpage, colorlinks=true,linkcolor= blue,citecolor=blue,urlcolor=lightblue}

\usepackage{jheppub}

@@

% \textwidth 16.9cm
% \oddsidemargin -.25cm

@@

% \renewcommand{\theequation}{\thesection.\arabic{equation}}
% \renewcommand{\theequation}{\arabic{equation}}

@@

\definecolor{wvvxds}{rgb}{0.396078431372549,0.3411764705882353,0.8235294117647058}
\definecolor{dbwrru}{rgb}{0.8588235294117647,0.3803921568627451,0.0784313725490196}
\definecolor{dtsfsf}{rgb}{0.8274509803921568,0.1843137254901961,0.1843137254901961}
\definecolor{wrwrwr}{rgb}{0.3803921568627451,0.3803921568627451,0.3803921568627451}
\definecolor{cqcqcq}{rgb}{0.7529411764705882,0.7529411764705882,0.7529411764705882}
\definecolor{rvwvcq}{rgb}{0.08235294117647059,0.396078431372549,0.7529411764705882}
\makeatletter

\newenvironment{calc}{\allowdisplaybreaks\start@align\@ne\st@rredtrue\m@ne}
{\addtocounter{equation}{1}\tag{\theequation}\endalign}
% for calculations/derivations---only last line gets an equation number, 
%	and allows page breaks for long calculations

@@

\date{\today}
\title{Stringy canonical forms and binary geometries from associahedra, cyclohedra and generalized permutohedra}

@@

% \baselineskip 24pt

\author[a,b]{Song He}
\author[a,b]{,\,Zhenjie Li}
\author[a,c,d]{,\,Prashanth Raman}
\author[a,b]{,\,Chi Zhang}
\affiliation[a]{CAS Key Laboratory of Theoretical Physics, Institute of Theoretical Physics, Chinese Academy of Sciences, Beijing 100190, China}
\affiliation[b]{School of Physical Sciences, University of Chinese Academy of Sciences, No.19A Yuquan Road, Beijing 100049, China}
\affiliation[c]{Institute of Mathematical Sciences, Taramani, Chennai 600 113, India}
\affiliation[d]{Homi Bhabha National Institute, Anushakti Nagar, Mumbai 400085, India}
\emailAdd{songhe@itp.ac.cn}
\emailAdd{lizhenjie@itp.ac.cn}
\emailAdd{prashanthr@imsc.res.in}
\emailAdd{zhangchi@itp.ac.cn}
\date{\today}
\abstract{Stringy canonical forms are a class of integrals that provide $\alpha'$-deformations of the canonical form of any polytopes. For generalized associahedra of finite-type cluster algebras, there exist completely rigid stringy integrals, whose configuration spaces are the so-called binary geometries, and for classical types are associated with (generalized) scattering of particles and strings. In this paper we propose a large class of rigid stringy canonical forms for another class of polytopes, generalized permutohedra, which also include associahedra and cyclohedra as special cases (type $A_n$ and $B_n$ generalized associahedra). Remarkably, we find that the configuration spaces of such integrals are also binary geometries, which were suspected to exist for generalized associahedra only. For any generalized permutohedron that can be written as Minkowski sum of coordinate simplices, we show that its rigid stringy integral factorizes into products of lower integrals for massless poles at finite $\alpha'$, and the configuration space is binary although the $u$ equations take a more general form than those ``perfect'' ones for cluster cases. Moreover, we provide an infinite class of examples obtained by degenerations of type $A_n$ and $B_n$ integrals, which have perfect $u$ equations as well. Our results provide yet another family of generalizations of the usual string integral and moduli space, whose physical interpretations remain to be explored. }

\maketitle

@@

The $u$ equations are:
\begin{align*}
&1-\tilde u_{[0,l]}=\left(\prod_{i=0}^{l-1} \prod_{j=i+1}^{k+1}  \tilde u_{[0,i]\cup [j,n]} \prod_{j=i+1}^{l+1} \tilde u_{[0,i]\cup [j,n]}\right) \left(\prod_{i=1}^{l+1} \prod_{j=l+1}^{n}\tilde u_{[i,j]} \right) \left(\prod_{i=1}^{k+1} \tilde u_{[i,n]} \right),\\[2ex]
&1-\tilde u_{[m+2,n]}=\left( \prod_{j=0}^{m}\tilde u_{[0,j]} \prod_{i=1}^{n-m-1}\tilde u_{[0,m+i]}^2 \right) \left( \prod_{i=m+1}^{n-1}\prod_{j=1}^{m+1}\tilde u_{[j,i]} \right) \left(\prod_{j=0}^{k-m-2} \prod_{i=1}^{m} \tilde u_{[0,i]\cup [3+j+m, n]} \prod_{i= m+1}^{j+m+1} \tilde u_{[0,i]\cup [3+j+m,n]}^2 \right) \\[2ex]
&1-\tilde u_{K_{l,m}}=\left(\prod_{a=0}^1\prod_{i=l+1}^{n}\tilde u_{[a,i]}\right) \left(\prod_{{\tiny {K_{l',m'} \not\subset K_{l,m}}\atop{K_{l,m} \not\subset K_{l',m'}} }} \tilde u_{K_{l',m'}}^{(l',m')||(l,m)}\right)\left(\prod_{j=2}^{m+1} \prod_{i=l+1}^{n} \tilde u_{[j,i]} \right)\times 
\begin{cases}
 1, ~{\rm if} ~ l=m  \\
 \prod_{i=0}^{l+1} \prod_{j=m+1}^n \tilde u_{[i,j]},~ {\rm if}~l \neq m
\end{cases}
\end{align*}
where $(l',m')||(l,m)$ is the compatability degree of $K_{l,m}$ with respect to $K_{l',m'}$ in $\mathscr B_n$ with the understanding that $\tilde u_{[0,n]}=1$ and the other $u$ equations are corresponding $u$ equations for $\mathscr A_n$ in new variables.

@@

\section{Stringy canonical forms and binary geometries for generalized permutohedra}
In this section we shall argue that a large class of generalized permutohedra which are realised as degenerations of permutohedron ${\mathscr P_n}$ are binary geometries. Before we proceed we shall review some details about the generalized permutohedra \cite{Postnikov:2005,Postnikov:2006} which we shall use throughout the paper.
\subsection{Generalized permutohedra}\label{GP}
A generalized permutohedron is a polytope that can be obtained as Minkowski sums and differences of co-ordinate simplices.

Let $\Delta_{[0,n]} = \operatorname{ConvexHull}(e_1,\dots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. Then we have:
\bea
{\mathscr P_n}(\{y_I \})= \sum y_I . \Delta_I  
\eea
for some collection of subsets $I \in [0,n]$.
We shall restrict ourselves to the large class of generalized permutohedra which admit such a realisation only as Minkowski sums except translations i.e, $y_I \ge 0$ for all non-singlets $I$~\footnote{This is mainly due to the subtle nature of the Minkowski difference operation, which makes the shape of the resulting polytope dependent on the relative magnitudes of $y_I$'s. We allow $y_I$ for singlets to be  negative as it is only a translation and to connect with \eqref{intgenperm}.} which are called nestohedra. Throughout the paper we shall mean nestohedra or products of nestohedra whenever we refer to generalized permutohedra.

The combinatorial structure of the generalized permutohedron ${\mathscr P_n(\{y_I\})}$ (nestohedra) is independent of $y_I$ and depends only on the collection of subsets $I \in [0,n]$ of the  building set ${\mathbf B}$, which is 
a collection of non-empty subsets of $[0,n]$ satisfying the following: %is called a building set ${\mathbf B} if it satisfies the following:
\begin{compactenum}[\quad (1)]
    \item If $I,J \in {\mathbf B}$ and $I \cap J \neq \varnothing $, then $I \cup J \in {\mathbf B}$.
    \item ${\mathbf B}$ contains all singletons $\{ i\}$ for $i \in S$.
\end{compactenum}
Here are some interesting examples of generalized permutohedra:
\begin{itemize}
    \item  If ${\mathbf B}= \{[i] | i=0,\dots,n \}$ is the complete flag of intervals, then ${\mathscr P_n(\{y_I\})}$ is the Stanley-Pitman polytope or Hypercube.
    \item If ${\mathbf B}$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ {\it i.e.}, the variables $Y_I$ are equal for all subsets of the same cardinality, then ${\mathscr P_n(\{y_I\})}$ is the usual permutohedron ${\mathscr P_n}$. 
    \item If ${\mathbf B}=\{ [i,j] | 0\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then ${\mathscr P_n(\{y_I\})}$ is the associahedron ${\mathscr A_n}$. 
    \item If  $\mathbf B=\{[i,i+k]\,:\,0\leq i, k\leq n\}$ is the set of cyclic intervals, then ${\mathscr P_n(\{y_I\})}$ is the cyclohedron ${\mathscr B_n}$.
    \item Let $\Gamma$ be a graph on the vertex set $[0,n]$. Let us assume that ${\mathbf B} = {\mathbf B}(\Gamma)$ is the set of subsets $I \in [0,n]$ such that the induced graph $\Gamma$ is connected, then  ${\mathscr P_n(\{y_I\})}$ is a graph associahedron.
\end{itemize}

\paragraph{Nested complex} To describe the combinatorial structure we need the notion of {\it nested complex}. We shall only summarize the necessary results here and let the reader interested in the details to refer \cite{Postnikov:2005,Postnikov:2006}.
A subset ${\mathbf N}$ in the building set ${\mathbf B}$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in {\mathbf N}$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\dots, J_k \in \mathbf N$ their union $J_1 \cup \cdots \cup J_k$ is not in $\mathbf B$.
    \item ${\mathbf N}$ contains all maximal elements of $\mathbf B$.
\end{compactenum}
The {\it nested complex} ${\mathbf N}({\mathbf B})$ is defined as the poset of the set of all nested sets in ${\mathbf B}$ ordered by inclusion.
\paragraph*{Facial structure} 
Let us assume that the set ${\mathbf B}$ associated with a generalized permutohedron ${\mathscr P_n(\{y_I\})}$ is a building set on $[0,n]$. \emph{Then the poset of faces ${\mathscr P_n(\{y_I\})}$ ordered by reverse inclusion is isomorphic to the nested complex ${\mathbf N}({\mathbf B})$}.

In particular, it means that (1) the set of facets of the generalized permutohedron just corresponds to the set of all elements in ${\mathbf B}$ excluding the maximal element, and (2) two facets corresponding to the sets $I$ and $J$ in ${\mathbf B}$ intersect {\it i.e.}, are {\it compatible} with each other, if and only if  either $I \subset J$,~ $J \subset I$~ or $I \cap J = \varnothing ~{\text and} ~ I \cup J \notin {\mathbf B}$.

@@

% Text Node
\draw (401.67,176.33) node [anchor=north west][inner sep=0.75pt]   [align=left] {01};
% Text Node
\draw (461,212) node [anchor=north west][inner sep=0.75pt]   [align=left] {0};
% Text Node
\draw (412,109) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
% Text Node
\draw (463,78) node [anchor=north west][inner sep=0.75pt]   [align=left] {12};
% Text Node
\draw (527,101) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
% Text Node
\draw (523,179) node [anchor=north west][inner sep=0.75pt]   [align=left] {02};
% Text Node
\draw (268,204) node [anchor=north west][inner sep=0.75pt]   [align=left] {0};
% Text Node
\draw (226,96) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
% Text Node
\draw (310,100) node [anchor=north west][inner sep=0.75pt]   [align=left] {12};
% Text Node
\draw (336,163) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
% Text Node
\draw (203,160) node [anchor=north west][inner sep=0.75pt]   [align=left] {01};
% Text Node
\draw (262,235) node [anchor=north west][inner sep=0.75pt]   [align=left] {(a)};
% Text Node
\draw (454,235) node [anchor=north west][inner sep=0.75pt]   [align=left] {(b)};
% Text Node
% \draw (155,263) node [anchor=north west][inner sep=0.75pt]   [align=left] {Figure showing the compatible\textbackslash incompatible facets of the 2d associahedron  \\ and permutohedron as generalized permutohedra};
\end{tikzpicture}
\end{center}
\caption{Facets of the 2d associahedron (a) and permutohedron (b) as generalized permutohedra}
\end{figure}

@@

The big polyhedron of generalized permutohedron is a simplex. Thus it's quite natural to wonder if the associated $u$ variables satisfy some kind of $u$ equations. We claim and we shall show in the next section that this is indeed the case. Further we show that all these polytopes are binary geometries even though some of them do not admit perfect $u$ equations.

@@

%We have seen that any $n$-dimensional generalized permutohedron can be constructed by a Minkowski sum of simplices labeled by subsets in the building set $\mathbf{B}$, which satisfy the conditions given above. 
As mentioned earlier, one can write down a natural stringy integral \eqref{intgenperm} for generalized permutahedron $\mathscr{P}(\bf B)$,
%it is a highly non-trivial fact about generalized permutohedra that the number of facets is given by $N=n+m$, where $m$ is the number of non-singletons in $\bf B$. 
%because each facet $F_I$ is given by a nested set $\{[0,n],I\}$ for $I\neq [0,n]$.
and its polytope is given by the Minkowski sum
\[
	\mathscr P_n(\{-S_I\,|\,I\in \mathbf B,\,|I|>1\}) =- \sum_{I\in\mathbf{B},|I|>1}S_I.\Delta_I,
\]
where $\Delta_I=\operatorname{ConvexHull}
(\{e_i\}_{i\in I})$ is the coordinate simplex in $(S_0,\dots,S_n)$-space, so the equation of the facet labeled by $I$ is given by eq.\eqref{eqoffacet}:
\begin{equation}\label{GPfacet}
	F_I:=\sum_{J\subset I,J\in\mathbf{B}}S_J=0.
\end{equation}
From the previous subsection we know that the big polyhedron of a generalized permutohedron is a simplex.
Therefore, we can write down the matrix $W^J_A$ of the facets and obtain  
\[
S_J=F_A(W^{-1})^A_J
\]
and 
its $u$ variables 
\[ u_A=\prod_J x_J^{(W^{-1})^A_J}. \]

Within generalized permutohedra, the original permutohedron is quite simple and important because any other generalized permutohedron can be obtained as a degenerated of the permutohedron.
The building set of the $n$-dimensional permutohedron $\mathscr P_n$ is 
the set of all non-empty subsets of $[0,n]$. 
To get $u$ equations, we should solve for $S_J$ from $F_J$ in eq.\eqref{GPfacet}, the 
solution for the permutohedron $\mathscr P_n$ is 
\begin{equation}\label{SinF}
	S_I=\sum_{J\subset I} (-1)^{|J|-|I|}F_J,
\end{equation}
This gives us the following ABHY polytope:
setting 
$S_I=-C_I$ for any non-singleton $I$, where $C_I$ are positive 
constants, and the polytope is given by the alternating sum
\begin{equation}\label{ABHY}
	F_I\geq 0,\quad -C_I=\sum_{J\neq \varnothing,J\subset I}(-1)^{|J|-|I|}F_J
\end{equation}
in the $\{F_I\}$-space.
By eq.\eqref{deffacet}, this polytope is the $n$-dimensional 
permutohedron $\mathscr P_n(\{C_I\})$, and it is nice that it admits a simple ABHY-like realization.
The ABHY construction of any generalized permutohedron can be obtained by 
setting $C_I=0$ in $\mathscr P_n(\{C_I\})$ for all $I$ not in its building set.

@@

Moreover, since we have found a variety of such geometries with perfect $u$ equations from degenerating ${\mathscr A}_n$ and ${\mathscr B}_n$, it'd be very interesting to explore more cases with perfect $u$ equations from degenerations of other types, {\it e.g.} ${\mathscr C_n}$ and ${\mathscr D_n}$. Along this direction, an intriguing possibility is to classify binary geometries with perfect $u$ equations from degenerating cluster cases; since any product of such geometries still has perfect $u$ equations, this amounts to find all elementary, non-factorizing geometries with perfect $u$ equations. More importantly,  what are the possible interpretations of these degenerations from cluster algebra; even for ${\mathscr A}_{n-3}$, what is the meaning of these degenerations of ${\cal M}_{0,n}$ and the string integrals?
